### 2023-10-13 chapters/background.tex
Work on discussion

Recently, several approaches for deep neural networks have been developed that address the rejection of samples $\xb\notin\mathcal{D}_{\text{in}}$. 
One way to categorize the different approaches is based on whether the underlying model is a classifier that estimates a conditional probability distribution $p(y|\xb)$ over some target variable $y$, or a model that learns a probability density $p(\xb)$ over the input itself. We might refer to the former as \emph{supervised} OOD detection, and the latter as \emph{unsupervised} OOD detection \parencite{graham_denoising_2023,liu_unsupervised_2023a}. It is important to note that this distinction relates only to the availability of some target value, $y$ - not whether OOD data is available for supervision\footnote{
    In our overview, we distinguish between supervised and unsupervised out-of-distribution by letting methods be classified as supervised that use any kind of target value $y$, whether it relates to the original task, available OOD data, or both. This is the same distinction made by \textcite{graham_denoising_2023} and \textcite{liu_unsupervised_2023a}. 
    However, it is important to note that in other works, the distinction is made based on whether the model is trained on OOD data or not \parencite{hendrycks_baseline_2017,liu_energy-based_2020}. This difference in nomenclature is currently unresolved in the literature. 
}. 
Supervised OOD detection tries to assess whether the model's prediction $\hat{y}$ via $p(y|\xb)$ should be trusted for a given input $\xb$, whereas unsupervised OOD detection judges whether the input $\xb$ should be trusted and used at all.

@@

\paragraph{Likelihood-based}
% \parencite{
%     X bishop_novelty_1994,
%     X choi_waic_2019,
%     X kirichenko_why_2020,
%     X ren_likelihood_2019,
%     X serra_input_2020,
%     X xiao_likelihood_2020,
%     X morningstar_density_2021,
%     X nalisnick_detecting_2019,
%     X bergamin_modelagnostic_2022,
%     X maaloe_biva_2019,
%     X havtorn_hierarchical_2021
% },
%
% Among the deep generative models that compute exact likelihoods are flow-based models, autoregressive models, and diffusion models, whereas variational autoencoders compute a lower bound on the likelihood, energy-based models usually require approximate methods, and generative adversarial networks do not compute an explicit likelihood at all.
\textcite{bishop_novelty_1994} first proposed to use the likelihood assigned to data by a generative model as a measure for detecting anomalous data. Simply put, since the likelihood measures ``how probable the data is'', OOD data is expected to give lower likelihoods than in-distribution data. Although, this method originally gave encouraging results, the advent of deep generative models and their application to high-dimensional data has lead many to observe likelihoods for OOD data that are higher than for in-distribution data \parencite{choi_waic_2019,nalisnick_detecting_2019,kirichenko_why_2020}. Such results have sparked interest in trying to explain this phenomenon and many works have proposed new scores for OOD detection derived from the likelihood.

>>>>

Recently, several approaches for deep neural networks have been developed that address the rejection of samples $\xb\notin\mathcal{D}_{\text{in}}$. 
One way to categorize the different approaches is based on whether the underlying model is a classifier that estimates a conditional probability distribution $p(y|\xb)$ over some target variable $y$, or a model that learns a probability density $p(\xb)$ over the input itself. We might refer to the former as \emph{supervised} OOD detection, and the latter as \emph{unsupervised} OOD detection \parencite{graham_denoising_2023,liu_unsupervised_2023a}. It is important to note that this distinction relates only to the availability of some target value, $y$ - not whether OOD data is available for supervision\footnote{
    In our overview, we distinguish between supervised and unsupervised out-of-distribution by letting methods be classified as supervised that use any kind of target value $y$, whether it relates to an original (in-distribution) task, available OOD data, or both. This is the same distinction made by \textcite{graham_denoising_2023} and \textcite{liu_unsupervised_2023a}. 
    It is important to note, however, that in other works, the distinction is made based on whether the model is trained on OOD data or not \parencite{hendrycks_baseline_2017,liu_energy-based_2020}. This difference in nomenclature is currently unresolved in the literature. 
}. 
Supervised OOD detection tries to assess whether the model's prediction $\hat{y}$ via $p(y|\xb)$ should be trusted for a given input $\xb$, whereas unsupervised OOD detection judges whether the input $\xb$ should be trusted and used at all.

@@

\paragraph{Likelihood-based}
% \parencite{
%     X bishop_novelty_1994,
%     X choi_waic_2019,
%     X kirichenko_why_2020,
%     X ren_likelihood_2019,
%     X serra_input_2020,
%     X xiao_likelihood_2020,
%     X morningstar_density_2021,
%     X nalisnick_detecting_2019,
%     X bergamin_modelagnostic_2022,
%     X maaloe_biva_2019,
%     X havtorn_hierarchical_2021
% },
%
% Among the deep generative models that compute exact likelihoods are flow-based models, autoregressive models, and diffusion models, whereas variational autoencoders compute a lower bound on the likelihood, energy-based models usually require approximate methods, and generative adversarial networks do not compute an explicit likelihood at all.
\textcite{bishop_novelty_1994} first proposed to use the likelihood assigned to data by a generative model as a measure for detecting anomalous data. Simply put, since the likelihood measures ``how probable the data is'', OOD data is expected to give lower likelihoods than in-distribution data. Although, this method originally gave encouraging results, the advent of deep generative models and their application to high-dimensional data has lead many to observe likelihoods for OOD data that are higher than for in-distribution data \parencite{choi_waic_2019,nalisnick_detecting_2019,hendrycks_deep_2019,kirichenko_why_2020}. Such results have sparked interest in trying to explain this phenomenon and many works have proposed new scores for OOD detection derived from the likelihood.

### 2023-10-13 chapters/conclusion.tex
Work on discussion

In the introductory \cref{chp:introduction} we laid out how, through human history, progress-driving technological development has always introduced new challenges and risks of error whether via misuse, misunderstanding or inherent limitations. We emphasized that machine learning comes with these same types of risk, in some cases amplifying their impacts, and argued that uncertainty estimation is a key component in ensuring that systems are safe and reliable in practice. We provided background for the research project by introducing the healthtech company Corti, with which with project has been defined and carried out, and the motivational cases of recognition of stroke cases in emergency calls (\cref{subsec:motivation-stroke-recognition}) and automated medical coding (\cref{subsec:motivation-medical-coding}). We described how machine learning systems could be designed to aid healthcare professionals with the tasks and gave examples of potential sources of uncertainty and of how correctly quantifying uncertainty might improve the usefulness of such systems. Finally, we connected machine learning reliability (\cref{sec:machine-learning-reliability}) and model calibration (\cref{subsec:model-calibration}) and defined the aleatoric, epistemic, and predictive types of uncertainty (\cref{subsec:understanding-uncertainty}).

@@

\dots

>>>>

In the introductory \cref{chp:introduction} we laid out how progress-driving technological development has always come with new challenges and risks of error - whether via misuse, misunderstanding or inherent limitations. We emphasized that machine learning comes with these same types of risk, in some cases amplifying their impacts, and argued that uncertainty estimation is a key component in ensuring that systems are safe and reliable in practice. We also provided the background for the research project by introducing the healthtech company Corti, with which with project has been defined and carried out, and the motivational cases of recognition of stroke cases in emergency calls (\cref{subsec:motivation-stroke-recognition}) and automated medical coding (\cref{subsec:motivation-medical-coding}). We described how machine learning systems could be designed to aid healthcare professionals with these tasks and gave examples of potential sources of uncertainty and of how correctly quantifying it might improve the usefulness of such systems. Finally, we drew connections between machine learning reliability (\cref{sec:machine-learning-reliability}) and model calibration (\cref{subsec:model-calibration}) and defined the aleatoric, epistemic, and predictive types of uncertainty (\cref{subsec:understanding-uncertainty}).

@@

In \cref{chp:paper-hierarchical}

In \cref{chp:paper-modelagnostic}

In \cref{chp:paper-benchmarking}
% In chapter 8, stochastic and deterministic generative models were benchmarked in terms of model likelihood. In addition, the chapter presented a hierarchical latent variable model (LVM) for speech inspired by the Clockwork VAE [238]. In contrast to self-supervised models, LVMs have not yet seen the same success for representation learning. As such, they offer little guidance in terms of alleviating the need for labeled data, as discussed in section 1.2.1.

% However, since LVMs learn a distribution over the training data, they are forced to encode all aspects of it. While this may be redundant for some tasks, others benefit from a broad variety of features. A hierarchical model that operates on multiple temporal scales, such as the Clockwork VAE, offers a natural way to encode different feature categories. Pronunciation might be learned at lower layers, speaker identity at the upper layers, and semantic features in between. Although some work has successfully separated speaker identity from content [114], models that can learn a deep hierarchy of features for speech remains an open challenge. The model presented in chapter 8 represents an effort to reignite this area of research.

\cref{chp:paper-review}
% Chapter 6 presented an overview of unsupervised neural speech representation learning. As emphasized in the overview, the wav2vec 2.0 framework [13], and masked pre-training in general, represent a breakthrough in low-resource speech recognition. The challenge associated with obtaining training data for conversational speech recognition, as discussed in section 1.2.1, has become much smaller. Even when no labeled in-domain data is available, this framework offers a viable solution [112].

% The general idea for masked pre-training may seem simple; reconstruct masked parts of the input or another representation, given context. However, this methodology aligns very well with the general definition of semantics presented in section 1.4: "semantic properties of a lexical item are fully reflected in appropriate aspects of the relations it contracts with actual and potential contexts" ([63], p. 1). Thus, from a philosophical point-of-view, it may be difficult to see how the field should move on from here. Of course, context is more than just the neighboring words in a speech segment. The next wave of representation learning for speech incorporates multiple modalities, such as video [244, 245] or text [18]. Furthermore, how to construct targets for pre-training these models and how that affects the learned features is an avenue that warrants more research. This is of particular interest in the speech domain, where the input codes for speaker identity and emotional state, as well as the semantic content of the utterance.

\cref{chp:paper-automated}

\cref{chp:paper-retrospective}

### 2023-10-13 chapters/discussion.tex
Work on discussion

During the three years since the start of this project, the rapid development of machine learning that started about a decade ago with the 2012 ImageNet competation and the work of \textcite{krizhevsky_imagenet_2012} all but slowed down. 
In this section we will briefly revisit selected chapters of the thesis and provide some additional thoughts and discussion.

\section{Speech representations and uncertainty}
%
In this thesis we have studied two different approaches to learning speech representations: VAEs in \cref{chp:paper-hierarchical,chp:paper-modelagnostic,chp:paper-benchmarking} and self"=supervised methods in \cref{chp:paper-review}. 
We found that the probabilistic formulation of VAEs provide benefits for their application to uncertainty quantification but that they are generally inferior to self"=supervised methods when it comes to performance on downstream tasks, such as phoneme recognition (see e.g. \cref{tab: phoneme recognition (PER), tab:unsupervisedASR}). 
Considering VAEs and self"=supervised methods, it seems we cannot build a model that has a principled probabilistic representation of uncertainty without sacrificing some of the ability to learn rich representations that are useful for downstream applications.

@@

One way to improve the representations learned in VAEs is via semi-supervised learning. 
Here a small number of labels are used to inform which patterns that are learned from a large, mostly unlabelled, data set. 
This is usually done by defining a new stochastic variable as the target and deriving a semi-supervised version of the ELBO that accomadates using the labels when they are available, or marginalizing the target variable when they are not. The VAE is then trained on the labelled and unlabelled data simultanously.

VAEs are strong models for semi-supervised learning as proven in several works \parencite{kingma_semi-supervised_2014,kingma_improved_2016,maaloe_biva_2019}. 
However, self"=supervised methods methods have established themselves as superior also in this setting \cite{jiang_speech_2021, liu_learning_2023}. 
Furthermore, by training on labelled and unlabelled data simultaneously, the semi-supervised setting of VAEs is more constraining than it is for self-supervised methods that divide the training into pre"=training and finetuning. Here, expensive pre"=training yields a single foundation model that can be fine"=tuned at relatively low cost for a large number of downstream tasks, while VAEs must learn all relevant downstream tasks while also learning from the unlabelled data, which is more expensive, but also requires retraining on the unlabelled data, when a .

Masking in variational autoencoders

Masked pre"=trained as maximum likelihood

@@

\section{\Cref{chp:paper-hierarchical} revisited: \dots}

\lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \parencite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}
\lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimizing a mutual information term in the ELBO (derive this form).}
\lesstodo[inline]{Discuss some recent work e.g. \cref{morningstar_density_2021}}

\section{\Cref{chp:paper-benchmarking} revisited: Bested?}

\lesstodo[inline]{Discuss whether variational autoencoders are viable for learning good representations for speech for downstream tasks when alternatives such as SSL method exist.}
\lesstodo[inline]{Out-of-distribution detection on speech?}

\section{\Cref{chp:paper-review} revisited: \dots} \label{sec:discussion-paper-review}

\lesstodo[inline]{Are self"=supervised speech representations useful for unsupervised uncertainty estimation? \parencite{nava_stateconsistency_2021, nava_uncertaintyaware_2021} Within robotics but not really related.}
% Since the main focus within self"=supervised learning has been on improving downstream task performance, very limited work, if any, has investigated self"=supervised representations in terms of uncertainty estimation. 
% However, in the context of medical applications where data can be abundant but labels are sparse, unsupervised uncertainty estimation is a very interesting direction for future work.
\lesstodo[inline]{OOD data: Generalization or detection (https://arxiv.org/pdf/2110.11334.pdf)?}

\section{\Cref{chp:paper-retrospective} revisited: Calibration}
Our work on stroke recognition in \cref{chp:paper-retrospective} focuses on the predictive performance of the ensemble model and an analysis of feature importance, but does not explicitly consider uncertainty estimation. 
As we discussed in \cref{subsec:model-calibration}, such a model can be calibrated to predict probabilities that are aligned with the empirical probability of the model being correct on some validation set. Here we present and discuss model calibration for the ensemble model.

@@

@@

\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curves_ensemble_with_cis.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}    
    % \hfill
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_fits_ensemble.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}    
    \caption[Calibration fits and curves for the stroke recognition ensemble using Platt-scaling and isotonic regression for calibration.]{ Calibration curves using sigmoid and isotonic calibration fits for the stroke recognition ensemble model (left) and the calibration fits (right) for the test set. We use the ensemble that achieved the median F1-score reported in \cref{fig_retrospective:figure1-roc-curve} and \cref{tab_retrospective:table3-occlusion-analysis}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic}
\end{figure}

@@

\begin{figure}
    % \begin{subfigure}[c]{0.48\columnwidth}
    %     \centering
    %     \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/precision_vs_predicted_probability_ensemble_calltaker_with_cis.pdf}
    %     % \caption{}
    %     % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    % \end{subfigure}    
    % % \hfill
    % \begin{subfigure}[c]{0.48\columnwidth}
    %     \centering
    %     \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/recall_vs_predicted_probability_ensemble_calltaker_with_cis.pdf}
    %     % \caption{}
    %     % \label{fig_discussion:histogram_ensemble_and_single_model}
    % \end{subfigure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/f1_score_vs_predicted_probability_ensemble_calltaker_with_cis.pdf}
        % \caption{}
        % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    \end{subfigure}    
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/predicted_probability_histogram.pdf}
        % \caption{}
        % \label{fig_discussion:histogram_ensemble_and_single_model}
    \end{subfigure}    
    \caption[Comparison of F1-score of stroke recognition ensemble and call-takers as function of predicted probability.]{ Comparison of the F1-score of the stroke recognition ensemble and call-takers. The F1-score is computed on subsets of the test dataset made by binning on the predicted probabilities of the calibrated ensemble. We see that the relative performance improvement of the ensemble over call-takers is higher towards more certain predictions. We use the ensemble that achieved the median F1-score reported in \cref{fig_retrospective:figure1-roc-curve} and \cref{tab_retrospective:table3-occlusion-analysis}.}
    \label{fig_discussion:retrospective-paper-f1-performance-vs-predicted-probability}
\end{figure}

% Inspecting the

% \todo[inline]{Finish this sentence and analysis.}

% Nevertheless, while correct calibration provides some explanation to the predictions, the actual value of the calibrated probabilities is still tied of the model's performance. By inspecting \cref{fig_discussion:retrospective-paper-f1-performance-vs-predicted-probability}, we can see that the logistic calibration shifts the predicted probabilities so far towards zero that the highest possible predicted probability is about 50\%. This means strokes can be predicted at best with a 50\% chance of being correct which limits the potential reduction in alarm fatigue.

% \todo[inline]{Finish this sentence and analysis.}

% Making matters worse, the most certain model predictions are the ones that agree the most with call-taker judgment (see \cref{fig_discussion:retrospective-paper-fractional-agreement-vs-probability}). Hence, keeping the most certain predictions also means reducing the potential for changing call-taker.. Not really if when the model disagrees at low prob it is always right while when it disagrees at high prob it is always wrong (although unlikely and contrary to calibration - but that was done for the total set of predictions, not subgroups)

% This highlights a problem where combining predictions with well-calibrated uncertainties may not be sufficient to ensure sustained use in practice.

% \lesstodo[inline]{Discuss the calibration of the stroke model and report calibration curve.}
% \lesstodo[inline]{Report the results of calibrating the stroke model using e.g. Platt scaling or Isotonic scaling.} % https://scikit-learn.org/stable/modules/calibration.html

>>>>

The last three years have seen the continuation of the rapid progress of machine learning that started about a decade ago with the 2012 ImageNet competation and the work of \textcite{krizhevsky_imagenet_2012}. The field of out-of-distribution detection saw a surge of interest following the papers by \textcite{choi_waic_2019,nalisnick_detecting_2019,hendrycks_deep_2019} and self"=supervised learning for speech has seen rapid advances with works such as CPC \parencite{oord_representation_2018}, wav2vec 2.0 \parencite{baevski_wav2vec_2020} and data2vec \parencite{baevski_data2vec_2022}.

Having focused in the previous chapters on VAEs for out-of-distribution detection and self"=supervised methods for representation learning, this chapter will add perspective on how VAEs might be enabled to learn representations more competetive with self"=supervised approaches, and how self"=supervised approaches might be used for out-of-distribution detection. 
Finally, we will discuss the use of calibration techniques for the stroke recognition model of \cref{chp:paper-retrospective}.

% Following the papers by \textcite{choi_waic_2019,nalisnick_detecting_2019,hendrycks_deep_2019}, the field of out-of-distribution detection saw a surge of new approaches using both generative models, supervised classifiers and self"=supervised representations. 
% Similarly, though the wave of works in self"=supervised learning might be traced back to \texttt{word2vec} of \textcite{mikolov_efficient_2013}, the impact of later works such as BERT \parencite{devlin_bert_2018} and GPT \parencite{radford_improving_2018} was immense and helped give rise to many approaches for self"=supervised learning for speech, including CPC \parecite{oord_representation_2018}, wav2vec 2.0 \parencite{baevski_wav2vec_2020} and data2vec \parencite{baevski_data2vec_2022}.
%

\section{Speech representations and uncertainty}
%
In this thesis we have studied two different approaches to learning speech representations: VAEs in \cref{chp:paper-hierarchical,chp:paper-modelagnostic,chp:paper-benchmarking} and self"=supervised methods in \cref{chp:paper-review}. 
We found that the probabilistic formulation of VAEs provide benefits for their application to uncertainty quantification but that they are generally inferior to self"=supervised methods when it comes to performance on downstream tasks, such as phoneme recognition (see e.g. \cref{tab: phoneme recognition (PER), tab:unsupervisedASR}). 
Considering VAEs and self"=supervised methods, it seems we have not yet been able to build a model that has a principled probabilistic representation of uncertainty without sacrificing some of the ability to learn rich representations that are useful for downstream applications.

@@

\paragraph{Semi-supervised learning} One way to improve the representations learned in VAEs is via semi-supervised learning. 
Here a small number of labels are used to inform which patterns that are learned from a large, mostly unlabelled, data set. 
This is usually done by defining a new stochastic variable as the target and deriving a semi-supervised version of the ELBO that accomadates using the labels when they are available, or marginalizing the target variable when they are not. The VAE is then trained on the labelled and unlabelled data simultanously.

VAEs are strong models for semi-supervised learning as proven in several works \parencite{kingma_semi-supervised_2014,kingma_improved_2016,maaloe_biva_2019}. 
However, self"=supervised methods methods have established themselves as superior for most tasks in this setting \cite{jiang_speech_2021, liu_learning_2023}. 
Furthermore, by training on labelled and unlabelled data simultaneously, the semi-supervised formulation for VAEs is more constraining than it is for self-supervised methods that divide the training into pre"=training and finetuning. The expensive pre"=training yields a single foundation model that can be fine"=tuned at relatively low cost for a large number of downstream tasks, whereas VAEs must learn all relevant downstream tasks while also learning from the unlabelled data. This is more expensive, but also requires retraining on the unlabelled data, when new supervised data becomes available.

\paragraph{Masking} As discussed in \cref{chp:paper-review}, one of the driving techniques behind the success of self"=supervised methods is masking \parencite{devlin_bert_2018,baevski_wav2vec_2020}. By removing tokens from the input or an early feature extraction layer and tasking a model with inferring their representations, the model is forced to learn how neighbouring tokens relate to those masked. Depending on the size of the mask, these dependencies can be more or less semantic in nature.

Different from self"=supervised methods, since VAEs learn the distribution over the training data, they are forced to encode all aspects important to it. 
As we also saw in \cref{chp:paper-hierarchical}, this will generally include low-level features that are important for accurate input reconstruction, but usually of lesser interest for downstream tasks. Furthermore, VAE reconstruction is performed based on latent variables which are inferred from the full, unmasked input.

Masking has only been sparsely examined for VAEs. One of the areas where it has seen the most attention is missing data imputation. In this setting, the input is partially observed, and often represented as a segmentation into observed and missing parts via a mask that indicates where the data is missing. The model is then trained to infer the latent variable from the observed data and reconstruction also deals only with the observed data. 
By comparison to self"=supervised approaches that use masking for representation learning, the missing data setting of VAEs focuses on reconstructing the observed data rather than the missing, which might lead to less useful representations. 
The idea of using VAEs to impute missing data was already examined in the seminal paper by \textcite{rezende_stochastic_2014}. Here the model was trained with fully observed data and used to impute data in an iterative sampling approach post hoc, leaving the learned representations unchanged.
Previous work that trains on partially observed data has largely focused on the ability of these models to yield high-quality imputations within the tabular and image data domains and have not probed for the effects on the learned latent representation \parencite{mattei_miwae_2019, ipsen_not-miwae_2021}.

@@

Uncertainty of representations versus uncertainty of downstream task outputs. 
% \textcite{wickstrom_relax_2023} propose a method for quantifying uncertainty based on

% \section{\Cref{chp:paper-hierarchical} revisited: \dots}

% \lesstodo[inline]{Discuss sensitivity to ``implicit" prior such as architecture (and probably optimization method and other). Include reference to \parencite{huszar_is_2017} discussing the usefulness of using a maximum likelihood objective for representation learning in generative models.}
% \lesstodo[inline]{Discuss whether VAEs are even suitable for representation learning due to them minimizing a mutual information term in the ELBO (derive this form).}
% \lesstodo[inline]{Discuss some recent work e.g. \cref{morningstar_density_2021}}

% \section{\Cref{chp:paper-benchmarking} revisited: Bested?}

% \lesstodo[inline]{Discuss whether variational autoencoders are viable for learning good representations for speech for downstream tasks when alternatives such as SSL method exist.}
% \lesstodo[inline]{Out-of-distribution detection on speech?}

% \section{\Cref{chp:paper-review} revisited: \dots} \label{sec:discussion-paper-review}

% \lesstodo[inline]{Are self"=supervised speech representations useful for unsupervised uncertainty estimation? \parencite{nava_stateconsistency_2021, nava_uncertaintyaware_2021} Within robotics but not really related.}
% % Since the main focus within self"=supervised learning has been on improving downstream task performance, very limited work, if any, has investigated self"=supervised representations in terms of uncertainty estimation. 
% % However, in the context of medical applications where data can be abundant but labels are sparse, unsupervised uncertainty estimation is a very interesting direction for future work.
% \lesstodo[inline]{OOD data: Generalization or detection (https://arxiv.org/pdf/2110.11334.pdf)?}

\section{\Cref{chp:paper-retrospective} revisited: Calibration}

Our work on stroke recognition in \cref{chp:paper-retrospective} focuses on the predictive performance of the ensemble model and an analysis of feature importance, but does not explicitly consider uncertainty estimation. 
As we discussed in \cref{subsec:model-calibration}, such a model can be calibrated to predict probabilities that are aligned with the empirical probability of the model being correct on some validation set. Here we present and discuss model calibration for the ensemble model.

@@

\begin{figure}
    \centering
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curves_ensemble_with_cis.pdf}
    \end{subfigure}    
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_fits_ensemble.pdf}
    \end{subfigure}    
    \caption[Calibration fits and curves for the stroke recognition ensemble using Platt-scaling and isotonic regression for calibration.]{ Calibration curves using sigmoid and isotonic calibration fits for the stroke recognition ensemble model (left) and the calibration fits (right) for the test set. We use the ensemble that achieved the median F1-score reported in \cref{fig_retrospective:figure1-roc-curve} and \cref{tab_retrospective:table3-occlusion-analysis}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic}
\end{figure}
\begin{figure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_curves_ensemble_with_cis.pdf}
    \end{subfigure}    
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/calibration_fits_ensemble.pdf}
    \end{subfigure}    
    \caption[Calibration fits and curves for the stroke recognition ensemble using Platt-scaling and isotonic regression for calibration.]{ Calibration curves using sigmoid and isotonic calibration fits for the stroke recognition ensemble model (left) and the calibration fits (right) for the test set. We use the ensemble that achieved the median F1-score reported in \cref{fig_retrospective:figure1-roc-curve} and \cref{tab_retrospective:table3-occlusion-analysis}.}
    \label{fig_discussion:retrospective-paper-calibration-curve-sigmoid-isotonic}
\end{figure}

@@

\begin{figure}
    % \begin{subfigure}[c]{0.48\columnwidth}
    %     \centering
    %     \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/precision_vs_predicted_probability_ensemble_calltaker_with_cis.pdf}
    %     % \caption{}
    %     % \label{fig_discussion:calibration_curve_ensemble_and_all_models_uncalibrated}
    % \end{subfigure}    
    % % \hfill
    % \begin{subfigure}[c]{0.48\columnwidth}
    %     \centering
    %     \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/recall_vs_predicted_probability_ensemble_calltaker_with_cis.pdf}
    %     % \caption{}
    %     % \label{fig_discussion:histogram_ensemble_and_single_model}
    % \end{subfigure}
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/f1_score_vs_predicted_probability_ensemble_calltaker_with_cis.pdf}
    \end{subfigure}    
    \begin{subfigure}[c]{0.48\columnwidth}
        \centering
        \includegraphics[width=1\columnwidth]{paper_retrospective_calibration_plots/predicted_probability_histogram.pdf}
    \end{subfigure}    
    \caption[Comparison of F1-score of stroke recognition ensemble and call-takers as function of predicted probability.]{ Comparison of the F1-score of the stroke recognition ensemble and call-takers. The F1-score is computed on subsets of the test dataset made by binning on the predicted probabilities of the calibrated ensemble. We see that the relative performance improvement of the ensemble over call-takers is higher towards more certain predictions. We use the ensemble that achieved the median F1-score reported in \cref{fig_retrospective:figure1-roc-curve} and \cref{tab_retrospective:table3-occlusion-analysis}.}
    \label{fig_discussion:retrospective-paper-f1-performance-vs-predicted-probability}
\end{figure}

@@
